\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{\articletitle}

### 2016-03-23 paper/paper.tex
stuff

\noindent Test

@@

%------------------------------------------------
\section{Introduction}
This paper will compare the time complexity of two color refinement algorithms and confirm them with computational results. The first algorithm uses the color refinement algorithm as shown by J. de Jong\cite{presentation:slidesPartI}, while the other algorithm is based on DFA minimization as shown by P. Bonsma\cite{presentation:slidesPartIII}. The algorithms have been implemented and their computation times on test sets will be used to confirm the time complexity.

@@

%------------------------------------------------
\section{Scope \& Objectives}
The aim of this research paper is to calculate and compare the worst-case time complexity of both color refinement algorithms and verifying them using computational results. These results will be used to examine the differences in computation time between the algorithms for different types of graphs.

This paper will describe both algorithms, give the calculations for the asymptotic worst-case time complexity, as well as an examination of the computational results.
%------------------------------------------------
\section{Methods}
%% TODO %%
% Describe experiment, setup, and method of testing
%%

%------------------------------------------------
\section{Algorithms}
%% TODO %%
% Describe algorithms, show concise calculations of time complexity
%%

%------------------------------------------------
\section{Results}
%% TODO %%
% Give and describe results
%%

%------------------------------------------------
\section{Discussion} %Change section name?
%% TODO %%
% Describe the effectiveness of the algorithms on various types of graphs, and examine the differences
%%

%------------------------------------------------
\section{Conclusions}
%% TODO %%
% Draw conlusions from both the results and discussion
%%

%----------------------------------------------------------------------------------------
%	REFERENCE LIST
%----------------------------------------------------------------------------------------

\printbibliography
%bibliography{references}

@@

\begin{appendices}
\end{appendices}
%----------------------------------------------------------------------------------------

>>>>

\noindent This will be the abstract of the paper

@@

%------------------------------------------------
\section{Introduction}
\label{intro}
This paper will compare the time complexity of two color refinement algorithms and confirm them with computational results. The first algorithm uses the color refinement algorithm as shown by J. de Jong\cite{presentation:slidesPartI}, while the other algorithm is based on DFA minimization as shown by P. Bonsma\cite{presentation:slidesPartIII}. The algorithms have been implemented and their computation times on test sets will be used to confirm the time complexity.

@@

%------------------------------------------------
\section{Scope \& Objectives}
\label{scope}
The aim of this research paper is to calculate and compare the worst-case time complexity of both color refinement algorithms and verifying them using computational results. These results will be used to examine the differences in computation time between the algorithms for different types of graphs.

This paper will describe both algorithms, give the calculations for the asymptotic worst-case time complexity, as well as an examination of the computational results.
%------------------------------------------------
\section{Methods}
\label{methods}
%% TODO %%
% Describe experiment, setup, and method of testing
%%

%------------------------------------------------
\section{Algorithms}
\label{algs}
%% TODO %%
% Describe algorithms, show concise calculations of time complexity
%%

%------------------------------------------------
\section{Results}
\label{results}
%% TODO %%
% Give and describe results
%%

%------------------------------------------------
\section{Discussion} %Change section name?
\label{disc}
%% TODO %%
% Describe the effectiveness of the algorithms on various types of graphs, and examine the differences
%%

%------------------------------------------------
\section{Conclusions}
\label{concl}
%% TODO %%
% Draw conlusions from both the results and discussion
%%

%----------------------------------------------------------------------------------------
%	REFERENCE LIST
%----------------------------------------------------------------------------------------
\label{references}
\printbibliography
%bibliography{references}

@@

\begin{appendices}
\label{appendices}
\end{appendices}
%----------------------------------------------------------------------------------------
